---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{css}

```

## Tracking study space conditions

This dynamic report tracks study space conditions using observations of available seats, observed activity, noise level, and time of day.

```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRkFZzJSUqhlUpl_1ivwLrWS3zQcWhlVfIyF-KC_Lhsbc6O3w4Mbp9x10NOvznU_efAe793qGk7aaAS/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    available_seats = 2,
    observed_activity = 3,
    noise_level = 4,
    time_of_day = 5
  )
```

The minimum number of available seats observed was `r min(latest_data$available_seats, na.rm = TRUE)`.

The average number of available seats observed was `r mean(latest_data$available_seats, na.rm = TRUE)`.

```{r}
ggplot(latest_data, aes(x = noise_level, fill = noise_level)) +
  geom_bar() +
  labs(
    title = "Count of observations by noise level",
    x = "Noise level",
    y = "Count",
    caption = "Source: logged_data"
  )
```

```{r}
ggplot(latest_data, aes(x = observed_activity, fill = observed_activity)) +
  geom_bar() +
  labs(
    title = "Count of observations by observed activity",
    x = "Observed activity",
    y = "Count",
    caption = "Source: logged_data"
  )
```
